{\fontfamily{ptm}\selectfont My Ideas after Reading Necoara's Papers}

### 2025-08-09 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main-2025-08-08.tex
=w=, changes after changes

        Then for all $x, y \in \RR^n$: 

@@

            - \frac{1}{2}\Vert \Pi_C x - \Pi_C y\Vert^2
            + \left\langle x - \Pi_C x, \Pi_C x - \Pi_C y\right\rangle

@@

            (\forall z \in \mathcal D(x | C))\; \mathcal D_\varphi(x, z) = \frac{1}{2}\Vert x - z\Vert^2 = D_f(z, x). 

@@

        The following assumption is about $(f, g, L_f, X^*)$. 

@@

    \begin{definition}[restricted QUA]

@@

        The function $F = f + g$ has restricted QUA condition if there exists $\kappa_f > 0, D \subseteq \dom g$ such that for all $x \in D$, let $\bar x = \Pi_{X^*}x$ it satisfies: 

@@

@@

    \subsection{examples for restricted QUA}
        The following assumption will characterize a specific type of convex programming problem that has relative quasi strong convexity. 
            Suppose $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
                \item $g = \delta_X(x)$ is the indicator function of $X \subseteq \RR^n$, where $X$ is a closed and convex, nonempty set. 
                \item The set $X^* = \Fix(\Pi_X \Pi_C) \neq \emptyset$. 
        We will show that, with additional assumptions, function in the above assumption can satisfy the restricted QUA conditions 
        \begin{theorem}[characterizing restricted QUA]\label{thm:example-rqua}

@@

            Then for all $x\in X$ such that $\Pi_{X^*} x\in \mathcal D(x | C)$, it has 

@@

                D_f(x, \Pi_{X^*}x) = \frac{1}{2}\Vert x - \Pi_{X^*} x\Vert^2 = D_f(\Pi_{X^*}x, x). 

>>>>

        Then for all $x, y \in \RR^n$, for all $\bar x \in \Pi_C x, \bar y \in \Pi_C y$, it satisfies: 

@@

            - \frac{1}{2}\Vert \bar  x - \bar  y\Vert^2
            + \left\langle x - \bar  x, \bar x - \bar y\right\rangle

@@

            (\forall z \in \mathcal D(x | C))\; \mathcal D_\varphi(x, z) = \frac{1}{2}\Vert x - z\Vert^2 = D_\varphi(z, x). 

@@

        The following assumption is about $(F, f, g, L_f, X^*)$. 

@@

    The limiting and regular subgradients are the same. 
    \begin{definition}[relatively restricted SCNVX]\label{def:rel-res-scnvx}

@@

        The function $F = f + g$ has restricted SCNVX condition if there exists $\kappa_f > 0, D \subseteq \dom g$ such that for all $x \in D$, let $\bar x = \Pi_{X^*}x$ it satisfies: 

@@

        The following assumption is about $(F, f, g, L_f, X^*)$. 
            \item Let $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. Following that, it has $X^* = \Fix(\Pi_X \Pi_C) \neq \emptyset$. 
            \item $g = \delta_X(x)$ is the indicator function of $X \subseteq \RR^n$, where $X$ is a closed and, nonempty set. 

@@

    \subsection{examples for restricted SCNVX}
        In the coming parts we look for conditions for which a function $F = f + g$ satisfying the above assumption also satisfies Definition \ref{def:rel-res-scnvx}. 
        \begin{theorem}[characterizing restricted SCNVX]\label{thm:example-rqua}

@@

            Then for all $x\in X, \bar x \in \Pi_{X^*} x$ such that $\bar x \in \mathcal D(x | C)$, it has 

@@

                D_f(x, \bar x) = \frac{1}{2}\Vert x - \bar x \Vert^2 = D_f(\bar x, x). 

### 2025-08-09 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
=w=, changes after changes

\section{Our crazy original ideas of extending their definitions}
    In this section, we will propose our ideas which relaxed Necoara's conditions for strong convexity.
    \begin{definition}[Breman Divergence for differentiable funtion]\label{def:bd}
        Let $f: \RR^n \rightarrow \RR$ be a $\mathcal C^1$ function. 
        The Bregman divergence is a $\RR^n \times \dom \nabla f(x)\rightarrow \RR$ mapping and, it's defined by:  
        \begin{align*}
            D_f(x, y) = f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 
        \end{align*}
    \end{definition}
    % ------------------------------------------------------------------------------------------------------------------
    \begin{theorem}[distance squared Bregman Divergence]\label{thm:bd-dist-sq}
        Let $C \subseteq \RR^n$ be any closed and non-empty. 
        Let $\varphi = (1/2)\dist(\cdot | C)^2$.
        Then for all $x, y \in \RR^n$: 
        \begin{align*}
            D_{\varphi}(x, y) 
            &= 
            - \frac{1}{2}\Vert \Pi_C x - \Pi_C y\Vert^2
            + \left\langle x - \Pi_C x, \Pi_C x - \Pi_C y\right\rangle
            + \frac{1}{2} \Vert x - y\Vert^2. 
        \end{align*}
    \end{theorem}
    \begin{proof}
        For notational simplicity let $\bar x = \Pi_C x, \bar y = \Pi_C y$. 
        Recall that $\nabla \varphi (x) = x - \bar x$. 
        With Definition \ref{def:bd} and, basic algebra we can show that: 
        \begin{align*}
            D_{\varphi}(x, y) &= 
            \varphi(x) - \varphi(y) - \left\langle \nabla \varphi(y), x - y\right\rangle
            \\
            &= \varphi(x) - \varphi(y) - \langle y - \bar y, x - y\rangle
            \\
            &= \frac{1}{2}(\Vert x - \bar x\Vert^2 - \Vert y - \bar y\Vert^2)
            - \langle y - \bar y, x - y\rangle
            \\
            &= \frac{1}{2}(\Vert x - \bar x\Vert^2 - \Vert y - \bar y\Vert^2)
            - \frac{1}{2}\Vert x - \bar y\Vert^2 
            + \frac{1}{2}\left(
                \Vert y - \bar y\Vert^2 + \Vert x - y\Vert^2
            \right)
            \\ 
            &= \frac{1}{2}\Vert x - \bar x\Vert^2
            - \frac{1}{2}\Vert x - \bar y\Vert^2 + \frac{1}{2}\Vert x - y\Vert^2
            \\
            &= 
            \frac{1}{2}\Vert x - \bar x\Vert^2
            - \frac{1}{2}\left(
                \Vert x - \bar x\Vert^2 + \Vert \bar x - \bar y\Vert^2
                + 2\langle x - \bar x, \bar x - \bar y\rangle
            \right)
            + \frac{1}{2}\Vert x - y\Vert^2
            \\
            &= - \frac{1}{2}\Vert \bar x - \bar y\Vert^2 + \langle x - \bar x, \bar x - \bar y\rangle 
            + \frac{1}{2}\Vert x - y \Vert^2. 
        \end{align*}
    \end{proof}
    \par
    In the parts that come, we will talk about the set of points that share the same projections onto a set.
    Let $C \subseteq \RR^n$, we define for all $x \in \RR^n$ the set: 
    \begin{align}
        \mathcal D(x | C) = \{z \in \RR^n : \Pi_C z = \Pi_C x\}. 
    \end{align}
    The following lemma is a precursor to extend the definition of Q-SCNVX. 
    The abbreviation ``DSBD'' stands for ``distance squared Bregman Divergence''. 
    % ------------------------------------------------------------------------------------------------------------------
    \begin{lemma}[conditions when DSBD behaves like norm squared]
        Let $C \subseteq \RR^n$ be closed and non-empty. 
        Let $\varphi = (1/2)\dist(\cdot | C)^2$.
        Then, for all $x \in \RR^n$ it satisfies
        \begin{align*}
            (\forall z \in \mathcal D(x | C))\; \mathcal D_\varphi(x, z) = \frac{1}{2}\Vert x - z\Vert^2 = D_f(z, x). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        The proof is direct. 
        For all $x \in \RR^n, z \in \mathcal D(x | C)$, the Bregman Divergence simplifies because using Theorem \ref{thm:bd-dist-sq} it has: 
        \begin{align*}
            D_\varphi (x, z) &= 
            - \frac{1}{2}\Vert \Pi_C x - \Pi_C z\Vert^2 
            + \langle x - \Pi_C x, \Pi_C x - \Pi_C z\rangle 
            + \frac{1}{2}\Vert x - z\Vert^2
            \\
            &= 0 + 0 + \frac{1}{2}\Vert x - z\Vert^2. 
        \end{align*}
        This is true because for all $z \in \mathcal D(x | C)$, it has $\Pi_C x - \Pi_C z = 0$. 
        Similarly, it has: 
        \begin{align*}
            D_\varphi(x, z) &= 
            - \frac{1}{2}\Vert \Pi_C x - \Pi_C z\Vert^2 
            + \langle z - \Pi_C z, \Pi_C z - \Pi_C x\rangle
            + \frac{1}{2}\Vert z - x\Vert^2
            \\
            &= 0 + 0 + \frac{1}{2}\Vert z - x\Vert^2. 
        \end{align*}
    \end{proof}
    \par
    Now, the definition of $\mathcal D(x | C)$ in the above lemma is nothing outrageous. 
    It simply denotes all points that share the same projection onto $C$ as $x$. 
    Below, we will give some possible scenarios. 
    \begin{enumerate}
        \item When $C$ is convex, the set $\mathcal D(x | C) = \Pi_C x + N_C(\Pi_C x)$. 
        \item When $C$ is nonconvex, it has $\mathcal D(x | C) \subseteq \Pi_C x + N_C(\Pi_C x)$. 
    \end{enumerate}
    Strong convexity is recovered when $C$ is a singleton. 
    For example when $C = \{\mathbf 0\}$, and $\varphi = (1/2)\Vert x\Vert^2$, this is the usual euclidean Bregman Divergence used to introduce functions that are strongly convex. 
    Furthermore, take note that $\Pi_C x \in D(x | C)$ always so, we have
    \begin{align}
        D_\varphi(x, \Pi_C x) = \frac{1}{2}\Vert x - \Pi_C \Vert^2 = D_\varphi(\Pi_C x, x). 
    \end{align}
    \par
    The following theorems will prepare us for linear convergence of first order algorithms. 
    \begin{definition}[proximal gradient operator]\label{def:pg}
        Let $F = f + g$, suppose that $f : \RR^n \rightarrow \RR$ is in $\mathcal C^1$ and $g: \RR^n \rightarrow \overline R$ is l.s.c. 
        The proximal gradient operator, denoted by $T_{B, f, g}$ is defined as
        \begin{align*}
            T_{B, f, g}(x) &= \argmin_{z\in \RR^n} \left\lbrace
                g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert x - z\Vert^2
            \right\rbrace
        \end{align*}
    \end{definition}
    \begin{remark}
        Usually we can find it in the literature that, $T_{B, f, g} = \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x))$. 
    \end{remark}
    The following assumption is the weakest and, it doesn't assume convexity at all. 
    \begin{assumption}[our assumptions]\label{ass:our-ass}
        The following assumption is about $(f, g, L_f, X^*)$. 
        \begin{enumerate}
            \item $f: \RR^n \rightarrow \RR$ is $L_f$ Lipschitz smooth. 
            \item $g: \RR^n \rightarrow \RR$ is l.s.c
            \item Denote $X^*$ be the fixed point set of $T_{L_f, f, g}$ and assume $X^* \neq \emptyset$. 
        \end{enumerate}
    \end{assumption}
    \begin{definition}[restricted QUA]
        Suppose that $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
        The function $F = f + g$ has restricted QUA condition if there exists $\kappa_f > 0, D \subseteq \dom g$ such that for all $x \in D$, let $\bar x = \Pi_{X^*}x$ it satisfies: 
        \begin{align*}
            \left(\forall v \in \partial F(\bar x)\right)\;
            F(x) - F(\bar x) - \langle v, x - \bar x\rangle 
            &\ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2. 
        \end{align*}
    \end{definition}
    \begin{remark}
        Take note that the RHS of the inequality $\kappa_f/2 \Vert x - \bar x\Vert^2 = D_\varphi(x, \Pi_{X^*}x)$ where $\varphi = (1/2)\dist(x | X^*)^2$. 
        This definition doesn't exclude nonconvex functions. 
        The hope is to have the set $D = \dom g$, but we don't think that is always true. 
        Our hope is that the set $D$ is at least somewhat larger than $X^+$. 
    \end{remark}
    The following discussion will give important consequences of this setup. 
    % ------------------------------------------------------------------------------------------------------------------
    \subsection{examples for relatively quasi strongly convex functions}
        The following assumption will characterize a specific type of convex programming problem that has relative quasi strong convexity. 
        \begin{assumption}[distance of two sets]
            Suppose $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
            In addition, we assume the following. 
            \begin{enumerate}[nosep]
                \item 
            \end{enumerate}
        \end{assumption}
        \begin{theorem}[example of restricted QUA]\label{thm:example-rqua}

        \end{theorem}
        \begin{proof}

        \end{proof}
    % ------------------------------------------------------------------------------------------------------------------
    \subsection{theorems useful for convergence analysis of algorithms}
        The proximal gradient inequality and, the Jensen inequality are the most important for deriving convergence rate of first order accelerated method.

>>>>

\section{Precurors materials for our proofs of linear convergence}
    We propose an alternative approach that extends the results, and make comparison with existing works from Necoara et al.
